% -*- TeX-master: "../dipole_ilya_paper.tex" -*-

\begin{thebibliography}{99}

\bibitem{linke2017} Linke,  Norbert M. and  Maslov, Dmitri and  Roetteler, Martin
  and Debnath, Shantanu and Figgatt, Caroline and Landsman, Kevin A.  and Wright,
  Kenneth  and  Monroe,  Christopher,  Proceedings of  the  National  Academy  of
  Sciences, \textbf{114}, 3305-3310 (2017)

\bibitem{gittins1989}  John  C  Gitins, Multi-armed  bandit  allocation  indices,
  Chichester, New York: Wiley, (1989)
        
\bibitem{reed2011} {M.  D. Reed,  L. DiCarlo,  S. E. Nigg,  L. Sun,  L.  Frunzio,
    S. M. Girvin and R. J. Schoelkopf}, Nature \textbf{482}, 382-385 (2011)

\bibitem{Astafiev2010} O. Astafiev  and A. M. Zagoskin and A.  A. Abdumalikov and
  Yu. A. Pashkin and T. Yamamoto and K.  Inomata and Y. Nakamura and J. S.  Tsai,
  Science, \textbf{327}, 5967 (2010)

\bibitem{hoi2011}  Hoi, Io-Chun  and Wilson,  C.  M.  and Johansson,  G\"oran and
  Palomaki,  Tauno and  Peropadre,  Borja  and Delsing,  Per,  Phys. Rev.  Lett.,
  \textbf{107}, 073601 (2011)

\bibitem{honigl2018} H\"onigl-Decrinis  T., Antonov I. V.,  Shaikhaidarov, R. and
  Antonov,  V. N.  and  Dmitriev, A.  Yu.  and  Astafiev, O.  V.,  Phys. Rev.  A,
  \textbf{98}, 041801 (2018)

\bibitem{shen2005}  Shen,   Jung-Tsung  and  Fan,  Shanhui,   Phys.   Rev.  Lett,
  \textbf{95}, 213001 (2005)

\bibitem{johnson2010}  {M.  W.   Johnson  and  P.   Bunyk  and  F.   Maibaum  and
    E. Tolkacheva  and A.  J.  Berkley and  E.  M. Chapple  and R. Harris  and J.
    Johansson and T. Lanting  and I.  Perminov and E.  Ladizinsky  and T.  Oh and
    G.  Rose}, {Supercond. Sci.  Technol.}, \textbf{23}, {065004} (2010)

\bibitem{phaseExp} Quantum processing involves manipulating the state of a qubit,
  $\Psi$, changing the relative state population, $\ensuremath{|\alpha|} \le 1$, and phase,
  $\varphi$, between the ground, \iket{0}, and excited, \iket{1}, states:
  \begin{equation}
    \label{eq:4}
    \Psi = \alpha\iket{0} + e^{i\varphi}(1-\alpha)\iket{1}.
  \end{equation}

  \noindent When  written as a  density matrix,  the phase information  is mapped
  onto the off-diagonal elements:
  \begin{equation}
    \label{eq:5}
    \rho = \iketbra{\Psi}{\Psi} = \begin{pmatrix}
      \iabsSquared{\alpha}  & \alpha(1-\alpha)e^{-i\varphi}\\
      \alpha(1-\alpha)e^{+i\varphi} & \iabsSquared{(1-\alpha)}.
    \end{pmatrix}
  \end{equation}

  \noindent The off-diagonal  elements decay to 1/e of the  initial value, over a
  time period $\tau_{\text{dec}}$ that can be measured experimentally.
    
\bibitem{monroe1995} {Monroe, C.  and Meekhof, D. M.  and King,  B. E. and Itano,
    W.   M. and  Wineland, D.  J.}, {Physical  Review Letters},\textbf{75},  4714
  (1995)

\bibitem{devoret2008}, {M. H. Devoret and A. Wallraff and J. M. Martinis} (2008)

\bibitem{orlando1999} {T.P. Orlando and J.E. Mooji and Lin Tian and Caspar H. van
    der Wal and L. Levitov and Seth Lloyd and J.J. Mazo}, {Science},\textbf{285},
  {1036} (1999)

\bibitem{chiorescu2003}  {I.  Chiorescu  and  Y.   Nakamura and  C.   J.  P.   M.
    Harmans and J. E. Mooij}, {Science}, \textbf{299}, 1869 (2003)

\bibitem{mooij1999} {Mooij,  J. E. and Orlando,  T. P. and Levitov,  L. and Tian,
    Lin  and  van   der  Wal,  Caspar  H.  and  Lloyd,   Seth},  {Science},  285,
  \textbf{5430} (1999)
	
\bibitem{cottet2002} A. Cottet, D. Vion, A.  Aassime, P.  Joyez, D.  Esteve, M.H.
  Devoret, Physica C: Superconductivity, \textbf{367}, 197 (2002)

\bibitem{gu2017} Gu,  Xiu and Kockum, Anton  Frisk and Miranowicz, Adam  and Liu,
  Yu-xi and Nori, Franco, Physics Reports, \textbf{718-719}, 1--102 (2017)

\bibitem{stern2014} Stern, M. and Catelani, G.   and Kubo, Y. and Grezes, C.  and
  Bienfait,   A.    and   Vion,   D.    and   Esteve,   D.   and    Bertet,   P.,
  Phys. Rev. Lett.,\textbf{113}, 123601 (2014)

\bibitem{yan2016}  Yan,  Fei  and  Gustavsson,   Simon  and  Kamal,  Archana  and
  Birenbaum,  Jeffrey and  Sears, Adam  P and  Hover, David  and Gudmundsen,  Ted
  J. and Rosenberg, Danna and Samach, Gabriel  and Weber, S and Yoder, Jonilyn L.
  and  Orlando, Terry  P.  and  Clarke, John  and Kerman,  Andrew J.  and Oliver,
  William D, Nature Communications, \textbf{7}, 12964 (2016)

\bibitem{qui2016} Yueyin Qiu and Wei Xiong and  Xiao-Ling He and Tie-Fu Li and J.
  Q. You, Scientific Reports, \textbf{6}, 28622 (2016)

\bibitem{pop2014} Pop, Ioan M. and  Geerlings, Kurtis and Catelani, Gianluigi and
  Schoelkopf, Robert  J. and Glazman, Leonid  I. and Devoret, Michel  H., Nature,
  508, \textbf{369} (2014)


\bibitem{zhu2010}   Zhu,Xiaobo    and   Kemp,Alexander   and    Saito,Shiro   and
  Semba,Kouichi, Applied Physics Letters, 97, \textbf{102503} (2010)


\bibitem{shulga2018} Original bad-ass paper


\bibitem{wu2013} {Yu-Lin Wu  and Hui Deng and Hai-Feng Yu  and Guang-Ming Xue and
    Ye Tian and Jie Li and Ying-Fei  Chen and Shi-Ping Zhao and Dong-Ning Zheng},
  {Chinese Physics B}, {22}, {060309} (2013)

\bibitem{earnest2018} C T Earnest et al 2018 Supercond. Sci. Technol. 31 125013
  
\bibitem{barends2011} {Barends,R.   and Wenner,J.   and Lenander,M.   and Chen,Y.
    and  Bialczak,R.   C.  and  Kelly,J.   and  Lucero,E.  and  O'Malley,P.   and
    Mariantoni,M.  and  Sank,D.  and  Wang,H. and White,T.   C.  and  Yin,Y.  and
    Zhao,J.  and  Cleland,A.  N.  and  Martinis,John M. and Baselmans,J.  J. A.},
  {Applied Physics Letters}, 99, {113507}, {2011}

\bibitem{abdumalikov2010} {Abdumalikov,  A.  A.  and Astafiev,  O.  and Zagoskin,
    A.  M.    and  Pashkin,  Yu.   A.  and  Nakamura,   Y.  and  Tsai,   J.  S.},
  {Phys. Rev. Lett.},104, {193601} (2010)

\bibitem{pi0_2006} https://arxiv.org/abs/cond-mat/0609441

\bibitem{manucharyan2009} {Vladimir  E. Manucharyan and  Jens Koch and  Leonid I.
    Glazman and Michel H. Devoret}, {Science}, \textbf{326}, 113 (2009)

\bibitem{devitt2016} Devitt, Simon J., Phys. Rev. A, {94}, {032329} (2016)

\bibitem{phase} Using  the commutation  relation for  conjugate number  and phase
  operators $ \left[\hat{n},\hat{\phi}\right] = 1 $
 
  {\scriptsize\begin{equation}\label{eq:ab1}
      \begin{aligned}
        \icommutation{\hat{\red{n}}}{e^{\pm i \hat{\blue{\phi}}}} & =  \icommutation{\hat{n}}{\sum_{\alpha = 0}^{\infty} \frac{(\pm i\hat{\blue{\phi}})^\alpha}{\alpha!}} = \sum_{\alpha = 0}^{\infty} (\pm i)^\alpha\frac{\icommutation{\hat{\red{n}}}{\hat{\blue{\phi}}^\alpha}}{\alpha!}\\
        & = \sum_{\alpha  = 0}^{\infty} (\pm i)^\alpha\frac{-\alpha i\hat{\blue{\phi}}^{\alpha -  1}}{\alpha!}  = \pm
        \sum_{\alpha = 1}^{\infty}i^{\alpha - 1}\frac{(\pm\hat{\blue{\phi}})^{\alpha - 1}}{(\alpha - 1)!}  = \pm
        e^{\pm i\hat{\blue{\phi}}}.
      \end{aligned}
    \end{equation}}
 
  \vspace{-1em}

  Operating with the number operator yields
  
  {\scriptsize \begin{equation}\label{eq:ab2}
      \begin{aligned}
        \hat{\red{n}}\bigg[e^{\pm  i\hat{\blue{\phi}}}\ket{n}\bigg]  =  &  \bigg[\pm
        e^{\pm i\hat{\blue{\phi}}}  + e^{\pm  i\hat{\blue{\phi}}}\hat{n}\bigg]\ket{n} =
        (n\pm 1)\bigg[e^{\pm i\hat{\blue{\phi}}}\ket{n}\bigg],
      \end{aligned}
    \end{equation}}

  meaning  that the  exponential  phase operator  is a  ladder  operator for  the
  \iket{n} state:

  \begin{equation}
    \label{eq:ab5}
    e^{\pm i\hat{\blue{\varphi}}}\ket{n} = \ket{n \pm 1} \Rightarrow e^{\pm i\blue{\varphi}} = \sum_{{i}} \iketbra{n_{i}\pm1}{n_i}.
  \end{equation}

  \vspace{-0.2em}
  
  \noindent Now phase a $\varphi_{2}$ operator can  be expressed in the number basis as
  follows: {\scriptsize
    \begin{equation}
      \label{eq:ab4}
      \cos(\varphi_{2})} = \frac{1}{2}\left(e^{i\varphi_{2}}+e^{-i\varphi_2}\right) = \frac{1}{2}\left(\sum_{{i}}\iketbra{n_{i}^{(2)}\pm 1}{n_{i}^{(2)}} \right)\otimes\mathbb{I}^{(1)}\otimes\mathbb{I}^{(3)}
  \end{equation}

  \noindent with $ \mathbb{I}^{(1)}=\sum_{i}\iketbra{n_{i}^{(1)}}{n_{i}^{(1)}} $ and
  $ \mathbb{I}^{(3)}=\sum_{i}\iketbra{n_{i}^{(3)}}{n_{i}^{(3)}} $ being the identity
  operators in the $ n^{(1)} $ and $ n^{(3)}$ subspaces.  }

\bibitem{rabi} The  Hamiltonian during  driving is a  combination of  the qubit's
  two-level system
  \begin{equation}
    \label{eq:rabi1}
    \mathcal{H}_{q} = -\frac{\hbar\omega_{21}}{2}\sigma_{z},
  \end{equation}

  \noindent                                                                 where
  $\sigma_z     =     \ensuremath{\left(\begin{smallmatrix}     1     &     0\\0     &
        -1 \end{smallmatrix}\right)} $, and the resonant drive of strength $ \hbar\Omega $

  \begin{equation}
    \label{eq:rabi2}
    \mathcal{H}_{d} = \hbar\Omega\cos(\omega_{21}t)\sigma_{x}
  \end{equation}

  \noindent  that  couples  the  two   levels  through  the  transition  operator
  $\sigma_x    =    \ensuremath{\left(\begin{smallmatrix}   0    &    1    \\   1    &
        0  \end{smallmatrix}\right)}  $.   Applying  the  unitary  transformation
  $    U(t)     =    \exp     \left(-i    \frac{\omega_{21}t}{2}\sigma_z\right)     $    to
  $ \mathcal{H} = \mathcal{H}_{q}+\mathcal{H}_{d} $ evaluates to

  \begin{equation}
    \label{eq:rabi3}
    \begin{aligned}
      \mathcal{H}'& = U\mathcal{H}U^{\dag} - i\hbar U\dot{U}^{\dag}\\
      & \approx \frac{\hbar\Omega}{2}\sigma_x
    \end{aligned}
  \end{equation}

  \noindent   under   the   approximation  that   non-conserving   energy   terms
  $ e^{\pm 2i\omega_{21}t}  $ are neglected. The  evolution of a ground  state in this
  rotated frame is
  \begin{equation}
    \label{eq:rabi4}
    \begin{aligned}
      U'(t)\iket{0} & = e^{-i\frac{\mathcal{H'}}{\hbar}t}\iket{0} \\
      & = \cos\left({\Omega t}/{2}\right)\ket{0}+i\sin\left({\Omega t}/{2}\right)\ket{1}.
    \end{aligned}
  \end{equation}

  \noindent  Rabi   oscillations  are   proportional  to  $   \iaverage{\sigma_{-}}  $
  \cite{Astafiev2010}, $\sigma_{-}~=~\iketbra{0}{1}$:

  \begin{equation}
    \label{eq:rabi5}
    \begin{aligned}
      \iaverage{\sigma_{-}} & = \bra{0}U'^{\dag}(t) \iketbra{0}{1} U'(t)\iket{0}\\
      & = \sin \left(\Omega t\right)
    \end{aligned}
  \end{equation}

\bibitem{gustavsson2012}  {Gustavsson, S.   and  Bylander, J.  and  Yan, F.   and
    Forn-D\'{\i}az, P.  and Bolkhovsky,  V.  and  Braje, D.   and Fitch,  G.  and
    Harrabi,  K. and  Lennon, D.  and Miloshi,  J. and  Murphy, P.  and Slattery,
    R.  and Spector,  S. and  Turek, B.  and  Weir, T.  and Welander,  P. B.  and
    Yoshihara,  F. and  Cory, D.   G. and  Nakamura, Y.  and Orlando,  T. P.  and
    Oliver, W. D.}, {Phys. Rev. Lett.}, \textbf{108}, 170503(2012)


  %% not used
  % \bibitem{Song2008} J.W. Song, N. A. Kabir, Y. Kawano,
  %   K. Ishibashi, G. R. Aizin, L. Mourokh, J. L. Reno, A. G. Markelz
  %   and J. P. Bird, App. Phys. Lett., \textbf{92}, 223115 (2008)
  % \bibitem{debnath2016} Debnath, S. and Linke, N. M. and Figgatt,
  %   C. and Landsman, K. A. and Wright, K. and Monroe, C., Nature,
  %   \textbf{536}, 63 (2016)


\end{thebibliography}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../dipole_ilya_paper"
%%% End:
