% -*- TeX-master: "../dipole_ilya_paper.tex" -*-

\begin{thebibliography}{99}

\bibitem{Astafiev2010} O.  Astafiev  and A.  M.  Zagoskin  and A.  A.  Abdumalikov  and Yu. A.
  Pashkin  and T.   Yamamoto and  K.  Inomata  and  Y.  Nakamura  and J.   S.  Tsai,  Science,
  \textbf{327}, 5967 (2010)

\bibitem{hoi2011} Hoi, Io-Chun and Wilson, C.   M.  and Johansson, G\"oran and Palomaki, Tauno
  and Peropadre, Borja and Delsing, Per, Phys. Rev.  Lett., \textbf{107}, 073601 (2011)

\bibitem{honigl2018} H\"onigl-Decrinis T., Antonov I.   V., Shaikhaidarov, R.  and Antonov, V.
  N.  and Dmitriev, A.  Yu.  and Astafiev, O.  V., Phys.  Rev.  A, \textbf{98}, 041801 (2018)

\bibitem{shen2005} Shen, Jung-Tsung  and Fan, Shanhui, Phys.  Rev.   Lett, \textbf{95}, 213001
  (2005)

\bibitem{johnson2010} {M.  W.  Johnson and P.  Bunyk  and F.  Maibaum and E. Tolkacheva and A.
    J.  Berkley and  E.  M.  Chapple and R.   Harris and J.  Johansson and T.   Lanting and I.
    Perminov  and E.   Ladizinsky  and T.   Oh  and G.   Rose},  {Supercond. Sci.   Technol.},
  \textbf{23}, {065004} (2010)
  
\bibitem{linke2017} Linke,  Norbert M. and Maslov,  Dmitri and Roetteler, Martin  and Debnath,
  Shantanu  and Figgatt,  Caroline and  Landsman, Kevin  A.  and  Wright, Kenneth  and Monroe,
  Christopher, Proceedings of the National Academy of Sciences, \textbf{114}, 3305-3310 (2017)

  % \bibitem{gittins1989} John C Gitins, Multi-armed bandit allocation indices,
  %   Chichester,
  %   New York: Wiley, (1989)
        
  % \bibitem{reed2011} {M.  D. Reed, L. DiCarlo, S. E. Nigg, L. Sun, L.  Frunzio,
  %   S. M. Girvin
  %   and R. J. Schoelkopf}, Nature \textbf{482}, 382-385 (2011)
    
\bibitem{monroe1995} {Monroe, C.  and Meekhof, D.  M.  and  King, B. E. and Itano, W.  M.  and
    Wineland, D.  J.}, {Physical Review Letters},\textbf{75}, 4714 (1995)

\bibitem{orlando1999} {T.P. Orlando and J.E. Mooji and Lin  Tian and Caspar H. van der Wal and
    L. Levitov and Seth Lloyd and J.J. Mazo}, {Science},\textbf{285}, {1036} (1999)

\bibitem{devoret2008}, {M. H. Devoret and A. Wallraff and J. M. Martinis} (2008)

\bibitem{chiorescu2003}  {I.  Chiorescu  and Y.   Nakamura  and C.   J.  P.   M.  Harmans  and
    J. E. Mooij}, {Science}, \textbf{299}, 1869 (2003)

\bibitem{mooij1999} {Mooij, J. E. and Orlando, T. P. and Levitov, L. and Tian, Lin and van der
    Wal, Caspar H.  and Lloyd, Seth}, {Science}, 285, \textbf{5430} (1999)
	
\bibitem{cottet2002} A.  Cottet, D.  Vion, A.   Aassime, P.  Joyez, D.  Esteve, M.H.  Devoret,
  Physica C: Superconductivity, \textbf{367}, 197 (2002)

\bibitem{gu2017} Gu, Xiu and Kockum, Anton Frisk and Miranowicz, Adam and Liu, Yu-xi and Nori,
  Franco, Physics Reports, \textbf{718-719}, 1--102 (2017)

\bibitem{stern2014} Stern, M. and Catelani, G.  and  Kubo, Y. and Grezes, C.  and Bienfait, A.
  and Vion, D.  and Esteve, D.  and Bertet, P., Phys. Rev. Lett.,\textbf{113}, 123601 (2014)

\bibitem{yan2016} Yan, Fei and Gustavsson, Simon and Kamal, Archana and Birenbaum, Jeffrey and
  Sears, Adam  P and  Hover, David  and Gudmundsen, Ted  J. and  Rosenberg, Danna  and Samach,
  Gabriel and  Weber, S and  Yoder, Jonilyn L.   and Orlando, Terry  P.  and Clarke,  John and
  Kerman, Andrew J.  and Oliver, William D, Nature Communications, \textbf{7}, 12964 (2016)

\bibitem{qui2016} Yueyin  Qiu and Wei  Xiong and Xiao-Ling  He and Tie-Fu  Li and J.   Q. You,
  Scientific Reports, \textbf{6}, 28622 (2016)

\bibitem{pop2014} Pop, Ioan  M. and Geerlings, Kurtis and Catelani,  Gianluigi and Schoelkopf,
  Robert J. and Glazman, Leonid I. and Devoret, Michel H., Nature, 508, \textbf{369} (2014)

\bibitem{shulga2018} Original bad-ass paper


\bibitem{wu2013} {Yu-Lin Wu  and Hui Deng and Hai-Feng  Yu and Guang-Ming Xue and  Ye Tian and
    Jie Li  and Ying-Fei  Chen and Shi-Ping  Zhao and Dong-Ning  Zheng}, {Chinese  Physics B},
  {22}, {060309} (2013)

\bibitem{earnest2018} C T Earnest et al 2018 Supercond. Sci. Technol. 31 125013
  
\bibitem{barends2011}  {Barends,R.    and  Wenner,J.    and  Lenander,M.   and   Chen,Y.   and
    Bialczak,R.   C.  and  Kelly,J.  and  Lucero,E.  and  O'Malley,P.  and  Mariantoni,M.  and
    Sank,D.  and Wang,H.  and  White,T.  C.  and Yin,Y.  and Zhao,J.   and Cleland,A.  N.  and
    Martinis,John M. and Baselmans,J.  J. A.}, {Applied Physics Letters}, 99, {113507}, {2011}

\bibitem{abdumalikov2010} {Abdumalikov,  A.  A.  and Astafiev,  O.  and Zagoskin, A.   M.  and
    Pashkin, Yu.  A.  and  Nakamura, Y.  and Tsai, J.  S.},  {Phys.  Rev. Lett.},104, {193601}
  (2010)

\bibitem{zhu2010}  Zhu,Xiaobo and  Kemp,Alexander and  Saito,Shiro and  Semba,Kouichi, Applied
  Physics Letters, 97, \textbf{102503} (2010)

  % \bibitem{pi0_2006} https://arxiv.org/abs/cond-mat/0609441

  % \bibitem{manucharyan2009} {Vladimir E. Manucharyan and Jens Koch and Leonid
  %   I.  Glazman and Michel H. Devoret}, {Science}, \textbf{326}, 113 (2009)

  % \bibitem{devitt2016} Devitt, Simon J., Phys. Rev. A, {94}, {032329} (2016)

\bibitem{gustavsson2012} {Gustavsson, S.   and Bylander, J.  and Yan,  F.  and Forn-D\'{\i}az,
    P.  and Bolkhovsky, V.  and Braje, D.  and  Fitch, G.  and Harrabi, K. and Lennon, D.  and
    Miloshi, J. and Murphy, P.  and Slattery, R.  and Spector, S.  and Turek, B.  and Weir, T.
    and Welander, P. B.  and Yoshihara, F.  and Cory, D.  G. and Nakamura, Y.  and Orlando, T.
    P.  and Oliver, W. D.}, {Phys. Rev. Lett.}, \textbf{108}, 170503(2012)

\bibitem{Bylander2011} Jonas  Bylander, Simon  Gustavsson, Fei  Yan, Fumiki  Yoshihara, Khalil
  Harrabi,  George Fitch,  David~G. Cory,  Yasunobu  Nakamura, Jaw-Shen  Tsai, and  William~D.
  Oliver.  \newblock  Noise spectroscopy through  dynamical decoupling with  a superconducting
  flux qubit.  \newblock {\em Nature Physics}, 7(7):565--570, may 2011.

\bibitem{Ithier2005}  G.~Ithier,  E.~Collin,  P.~Joyez,  P.~J.   Meeson,  D.~Vion,  D.~Esteve,
  F.~Chiarello, A.~Shnirman, Y.~Makhlin, J.~Schriefl,  and G.~Schön.  \newblock Decoherence in
  a superconducting quantum bit circuit.  \newblock {\em Physical Review B}, 72(13), oct 2005.

\bibitem{Martinis2003}  John~M. Martinis,  S.~Nam, J.~Aumentado,  K.~M.  Lang,  and C.~Urbina.
  \newblock Decoherence of a superconducting qubit due to bias noise.  \newblock {\em Physical
    Review B}, 67(9), mar 2003.
  
  %% not used
  % \bibitem{Song2008} J.W. Song, N. A. Kabir, Y. Kawano,
  %   K. Ishibashi, G. R. Aizin, L. Mourokh, J. L. Reno, A. G. Markelz
  %   and J. P. Bird, App. Phys. Lett., \textbf{92}, 223115 (2008)
  % \bibitem{debnath2016} Debnath, S. and Linke, N. M. and Figgatt,
  %   C. and Landsman, K. A. and Wright, K. and Monroe, C., Nature,
  %   \textbf{536}, 63 (2016)

  % \bibitem{lor5b}
  %   http://microchem.com/pdf/PMGI-Resists-data-sheetV-rhcedit-102206.pdf
  
  % \bibitem{s1813}
  %   http://www.nanophys.kth.se/nanophys/facilities/nfl/resists/S1813/s1800seriesDataSheet.pdf

  % \bibitem{mf319}
  %   \href{http://microchem.com/products/images/uploads/MF_319_Data_Sheet.pdf}{datasheet}
\end{thebibliography}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../dipole_ilya_paper"
%%% End:
